Usage metrics

### 2021-04-12 analysis/corpus.Rmd
Fixes in S4 and new data

BASE_packages <- read_lines(BASE_CORPUS_FILE)
BASE_evals_per_package <- read_csv(BASE_EVALS_STATIC_FILE, col_types = cols(
  package = col_character(),
  fun_name = col_character(),
  srcref = col_character(),
  call_fun_name = col_character(),
  args = col_character()
))

@@

### Matching evals

```{r}
matched_eval_callsites <-
  left_join(
    CRAN_eval_callsites, 
    count(CRAN_eval_traces, eval_call_srcref), 
    by=c("srcref"="eval_call_srcref")
  ) %>%
  mutate(
    n=replace_na(n, 0)
  ) %>%
  rename(hit=n)
```

The dynamic analysis traced `r fmt(ratio(filter(matched_eval_callsites, hit>0), matched_eval_callsites))`

>>>>

BASE_packages <- read_lines(BASE_CORPUS_FILE)
BASE_evals_per_package <- read_csv(
  BASE_EVALS_STATIC_FILE, 
  col_types = cols(
    package = col_character(),
    fun_name = col_character(),
    srcref = col_character(),
    call_fun_name = col_character(),
    args = col_character()
  )
)

@@

### 2021-04-12 analysis/usage.Rmd
Fixes in S4 and new data

overview_table(
  r("Allcalls", nb_calls),
  r("Evals", eval_calls),
  r("Evalqs", evalq_calls),
  r("Eparents", eval.parent_calls),
  r("Locals", local_calls),
  r("Triggeredpkgs", length(unique(E$ev_package)))
) -> TBL
```

>>>>

overview_table(
  r("Allcalls", nb_calls),
  r("Evals", eval_calls),
  r("Evalqs", evalq_calls),
  r("Eparents", eval.parent_calls),
  r("Locals", local_calls),
  r("Triggeredpkgs", length(unique(E$ev_package))),
  r("EvalsRatio", ratio(eval_calls, nb_calls)),
  r("EvalqsRatio", ratio(evalq_calls, nb_calls)),
  r("EparentsRatio", ratio(eval.parent_calls, nb_calls)),
  r("LocalsRatio", ratio(local_calls, nb_calls)),
) -> TBL
```
